A formal approach but practical approach in train regulation

### 2025-06-24 paper/main.tex
Suppression grammaire

Given a routing program $E$, $\handlerOf{E}{\tid{id}}$ is the list of handlers of train $\tid{id}$, $\head{\handlerOf{E}{\tid{id}}}$ is the handler of the first event for that train.

The syntax of each handler is given by the non-terminal {\ttfamily stmt} in Grammar~\ref{gr:regulator_program}.\todo{est-ce toujours nécessaire maintenant que les handlers sont dans un liste ?}
The program of the regulator is a set of rules, guarded by events. A rule $\ev{\tid{id}}{n}{A}$ denotes that upon entering the $n$-th block of its route, train $\tid{id}$ will trigger actions $A$. The list of actions in the handler are of four kinds: 
\begin{description}
	\item[\incr{\bid{id}}:] this updates the token $\bid{id}$ in $T$:  $T \cdot \incr{\bid{id}}  \triangleq T[\bid{id} \leftarrow T(\bid{id})+1]$
	\item [\wait{\bid{id}}{i}:] ...\todo{}
	\item [\turn{\sid{id}}{s}:] this instructs the regulator to turn the switch $\sid{id}$ into the $s$ state: $\sigma\cdot\turn{\sid{id}}{s} = \sigma[\sid{id} \leftarrow s]$
	\item [\auth:] ...\todo{}
\end{description}

@@

\begin{grammar}[Regulator's rules, with $\tid{id} \in \trains$, $n \in  \Nat$, $\bid{id} \in \blocks$, $\sid{id} \in \turnouts$, $s\in \internalState$.][h][gr:regulator_program]
	\firstcasesubtil{\ttfamily stmt}{\evGuard{\tid{id}}{n} : \nonterm{A}^\star}{}
	\firstcase{A}{\incr{\bid{id}}}{}
	\otherform{\wait{\bid{id}}{i}}{}
	\otherform{\turn{\sid{id}}{s}}{}
	\otherform{\auth}{}
\end{grammar}

>>>>

Given a routing program $E$, $\handlerOf{E}{\tid{id}}$ is the list of handlers of train $\tid{id}$, $\head{\handlerOf{E}{\tid{id}}}$ is the handler of the first event for that train.
The handler for a given event is a list of actions, each of them being one of the following:
\begin{description}
	\item [\wait{\bid{id}}{n}:] the train waits until the token of block \bid{id} reaches value $n$
	\item [\incr{\bid{id}}:] this increments the token $\bid{id}$ in $T$, thus releasing a train waiting
	\item [\turn{\sid{id}}{s}:] this turns the switch $\sid{id}$ into the $s$ state: $\sigma\cdot\turn{\sid{id}}{s} = \sigma[\sid{id} \leftarrow s]$
	\item [\auth:] a shortcut for waiting on oneself
\end{description}

@@
